SAT Competition 2020\tnoteref{title}

### 2020-12-18 paper/main.tex
small refinements in section 3

In the Incremental Library track we mimic scenarios
where a SAT solver is used as a backend solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. Incrementality means that
the individual calls to the SAT solver are not independent, but may share 
a common subset of the input clauses or differ in the presence of additional 
unit clause assumptions \cite{TODO}.

@@

For selection of benchmark instances in this competition, we used GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}}. 
GBD Tools is a tool-chain for maintenance and distribution of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
Its database\footnote{\url{https://gbd.iti.kit.edu}} contains information about all instances used in SAT competitive events dating back to 2006. 
In GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.

Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.
Like this it is possible to query for instances with desired properties, e.g., instance author, family and result, which gives the instance selection process a new quality.

@@

The ``Bring Your Own Benchmarks'' (BYOB) rule (applied as of SAT Competition 2017~\cite{SC2017}) requires solver authors to submit $20$ new benchmark instances in order to participate in the competition. At least $10$ of these instances are required to be ``interesting'', whereby interesting is defined as Minisat~\cite{Niklas:2003:Minisat} needs at least one minute to solve it and the authors own solver does not run into a timeout for the instance.

In total, $28$ authors followed our calls for participation and benchmark instances, thus contributing to a set of $1260$ previously unseen benchmark instances with a variety of $27$ different instance families. 
By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances.

In order to compile a balanced set of $300$ benchmark instances, we used the procedure which is depicted in Algorithm~\ref{algo:select} to select a maximium of $14$ submissions per author. 
Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.

>>>>

In the Incremental Library track we mimic scenarios
where a SAT solver is used as a backend solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. Incrementality means that
the individual calls to the SAT solver are not independent, but may share 
a common subset of the input clauses or differ in the presence of additional 
unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.

@@

For selection of benchmark instances in this competition, we used GBD Tools.%
\footnote{\url{https://pypi.org/project/gbd-tools/}} 
Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with desired properties, e.g., instance author, family and result.
The association of instance-id and instance attributes is maintained in publicly available databases.%
\footnote{\url{https://gbd.iti.kit.edu}}

GBD Tools is a tool-chain for maintenance and distribution of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
Its databases provide information about all instances used in SAT competitive events dating back to 2006. 
In GBD Server, each instance also has an URL, such that instances can be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.

@@

The ``Bring Your Own Benchmarks'' (BYOB) rule is established since SAT Competition 2017~\cite{SC2017}. 
By this rule solver authors are required to submit $20$ new benchmark instances in order to participate in the competition. At least $10$ of these instances are required to be ``interesting'', meaning that Minisat must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.

As can be seen in Table~\ref{tab:families}, a total of $28$ authors followed our calls for participation and benchmark instances, thus contributing a set of $1260$ previously unseen benchmark instances in a large variety of different instance families.

By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances. 
In order to compile a balanced set of $300$ benchmark instances, we considered a maximium of $14$ submissions per author and used the procedure which is depicted in Algorithm~\ref{algo:select}. 
Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
